% An in-depth explanation of the problem, including the "business case". What is wrong with the status-quo or what opportunity exists that justifies undertaking this project (expanding upon the problem statement)? If you have a clear customer or sponsor, why do they want you to work on this? What is the existing relationship, if any, between the development team and the customer? This section should occupy 1/2 - 1 full page.

Currently, on the longboard market, there are two options: a normal longboard and an electric longboard. What we are introducing is a better version of an electric longboard. In addition to being controlled like an electric longboard, this product will add a level of autonomy to the longboard. 

% A few of the issues that come with owning a longboard are having to carry it around when it is not being used and having to remember where it is placed when not in use. Our product solves both of these problems with its autonomy: the ability to summon the board and the ability to follow a target.

There are a few issues that come with owning a longboard. One of these issues is having to carry the board around when it is not is use. A longboard is fairly large and it takes effort and energy to carry it. Another issue is having to remember where a long board is placed when it is not in use. The product we are introducing tackles these problems. One of the features our product introduces is the ability to summon the board from wherever it may be within a certain radius. This eliminates the problem of not knowing where a board has been left when it is no longer in use. Another feature our product introduces is the ability to lock onto a target and follow them as they move. This feature solves having to carry the board everywhere you go.

Most electric longboards are controlled by little remotes. There are a few issues that can come with remote controllers. Remotes can be lost and the internal batteries can be drained. To alleviate this, we are introducing an app that would control the longboard. With an app to control the board, the user will not have to worry about charging/changing the batteries or losing their remote as it will be integrated in their phones, an important part of everyday life.
% don't hate me, I took a few liberties <3 KB